---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(rtist)
```

# rtist

<!-- [![Travis build status](https://travis-ci.org/tomasokal/rtist.svg?branch=master)](https://travis-ci.org/tomasokal/rtist) -->
<!-- [![Dependencies](https://tinyverse.netlify.com/badge/rtist)](https://cran.r-project.org/package=rtist) -->
<!-- [![CRAN status](http://www.r-pkg.org/badges/version/rtist)](https://cran.r-project.org/package=rtist) -->
<!-- [![Downloads](http://cranlogs.r-pkg.org/badges/rtist?color=brightgreen)](http://www.r-pkg.org/pkg/rtist) -->

## Overview

Can use to pull historical draft data from [Pro Football Reference](https://www.pro-football-reference.com/).

## Installation

Install from Github.

``` {r, eval = FALSE}
# Install remotes to download.
install.packages("remotes")

# And then install from github.
remotes::install_github("tomasokal/nfldraftr")
```

## Draft Years

`nfldraftr` provides historical draft data that can be accessed one year at a time or through a range of years.

``` {r year, eval = TRUE}
# Load package
library(nfldraftr)

# Draft data from 2020
nfldraftr::draft_year(year = "2020")
```

``` {r range, eval = TRUE}
# Draft data from 2020
nfldraftr::draft_range(min = "2015", max = "2020")
```

Data is pulled in to feature draft year, pick round, overall pick number, team, player, position, age, and college.

## Credits

All data is pulled from [Pro Football Reference](https://www.pro-football-reference.com/). Accuracy of this data is dependent on the source.



