---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(nfldraftr)
library(kableExtra)
library(knitr)
```

# nfldraftr

<!-- badges: start -->
  [![R build status](https://github.com/tomasokal/nfldraftr/workflows/R-CMD-check/badge.svg)](https://github.com/tomasokal/nfldraftr/actions)
<!-- badges: end -->

## Overview

Can use to pull historical draft data from [Pro Football Reference](https://www.pro-football-reference.com/).

## Installation

Install from Github.

``` {r, eval = FALSE}
# Install remotes to download.
install.packages("remotes")

# And then install from github.
remotes::install_github("tomasokal/nfldraftr")
```

## Draft Years

`nfldraftr` provides historical draft data that can be accessed one year at a time or through a range of years.

``` {r year, eval = TRUE}
# Load package
library(nfldraftr)

# Draft data from 2020
draft2020 <- nfldraftr::draft_year(year = "2020")
head(draft2020) %>% 
  kable(row.names = FALSE) 
```

``` {r range, eval = TRUE}
# Draft data from 2020
df_draft_range <- nfldraftr::draft_range(min = "2015", max = "2020")
df_draft_range <- df_draft_range[order(df_draft_range$OVERALL_PICK), ]
head(df_draft_range) %>% 
  kable(row.names = FALSE) 
```

Data is pulled in to feature draft year, pick round, overall pick number, team, player, position, age, and college.

## Credits

All data is pulled from [Pro Football Reference](https://www.pro-football-reference.com/). Accuracy of this data is dependent on the source.



